---
title: |
  | \textbf{Covid-19 Briefing South Tyrol}
  | Executive Summary
author: | 
  | \textsc{Thomas Ludwig}
  | thomas.ludwig95@gmail.com
date: "`r format(Sys.time(), '%d. %B %Y')`"
output: 
  beamer_presentation:
    keep_tex: false
    slide_level: 2
    toc: false
    theme: "boxes"
    colortheme: "dove"
header-includes:
- \usepackage[german]{babel}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage[hang, small, bf, margin=20pt, tableposition=top]{caption}
- \setlength{\abovecaptionskip}{0pt}
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

library(kableExtra) # nice tables

# source script with analysis
source("covid_analysis.R", encoding = "UTF-8")

```

## Covid-19 Briefing South Tyrol

- Summary of most important drivers of Covid-19 pandemic for South Tyrol
- Data is obtained from: http://www.provinz.bz.it/sicherheit-zivilschutz/zivilschutz/coronavirus.asp
- Population data for 7 day incidence calculation is taken from: https://de.wikipedia.org/wiki/Bezirksgemeinschaft
- Parametric estimation of $\text{R}_\text{eff}$ is provided
- I use *EpiEstim* package (https://cran.r-project.org/web/packages/EpiEstim/index.html)
- Parameters might me biased because of mutations $\rightarrow$ **$\text{R}_\text{eff}$ only indicative!**
- **Please consider disclaimer on last page!**


## Smoothed Raw Data New Cases

```{r, echo=FALSE}

plot_smooth

```

## Daily Incidence South Tyrol

```{r, echo=FALSE}

incidence_daily

```


## Overall 7-day incidence per 100k South Tyrol

```{r, echo=FALSE}

seven_day

```

## 7-day incidence per 100k Details

```{r, echo=FALSE}

seven_day_all

```


## Estimation of $\text{R}_\text{eff}$

- I use approach proposed by Cori et al. (2013)
- Implemented in **EpiEstim** R package
- I use parametric approach for serial interval
- *Offset Gamma distribution* is used for the serial interval
- Estimation window: sliding weekly windows
- No explicit estimation of parameters
- I use best practice parameters for Covid-19 pandemic:
- Mean: 4.8
- Standard Deviation: 2.3

## $\text{R}_\text{eff}$ Estimation Results for South Tyrol

```{r, echo=FALSE}

r_eff

```


## $\text{R}_\text{eff}$ Detail Table

```{r, echo=FALSE}

kable(tbl_r, "latex", booktabs = T, caption = "R Estimation South Tyrol",
      digits = 3, format.args = list(big.mark = ","), linesep = "") %>%
  kable_styling(position = "center", latex_options = "hold_position")

```


## Summary of $\text{R}_\text{eff}$ Estimation

```{r, echo=FALSE}

plot(res_parametric_si)

```


## Disclaimer

- All results are illustrative - no claim to completeness of analysis
- Results don't necessarily match official data
- Different data and calculations to official data possible
- All errors are my own
